%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{cv} % Use the custom cv.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Leander Hutton} % Your name
\address{10699 NC HWY 194 N \\ Todd, NC 28684} {
\address{(828)~$\cdot$~719~$\cdot$~7826 \\ leander@one-button.org} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Appalachian State University} \hfill {\em Degree Awarded - May 2011} \\ 
{\em Masters of Science in Physics and Laboratory Automation} \\
Member of Sigma Pi Sigma - Physics Honors Society \\
Research on astrophysics applications of GPGPU technology \\
Instrumentation and automation focus \\

{\bf Appalachian State University} \hfill {\em Degree Awarded - May 2008} \\ 
{\em Bachelor of Science in Physics \& Astronomy} \\
Collected and reduced data on binary asteroids \\
Publication of data in ICARUS \\
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Appalachian State University Physics and Astronomy}{August 2013 - Present}{Adjunct Faculty - Astronomy Lab Instructor}{Boone, NC}
\item Teaching introductory astronomy concepts to students; providing and evaluating hands-on exercises.
\item Operated the Rankin GoTo Astronomy Lab consisting of several Celestron SCTs and SBIG imaging cameras.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University ITS - NICS}{November 2013 - Present}{Network Specialist}{Boone, NC}
\item Performed system administration tasks on Linux and BSD based systems.
\item Installed and maintained a variety of applications; including but not limited to nginx, Apache, MySQL, OpenVPN, Cacti, MRTG, and PostgreSQL.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University ITS - Enterprise Systems}{February 2010 - November 2013}{Operations and Systems Analyst}{Boone, NC}
\item Performed system administration tasks on Linux based systems.
\item Installed and maintained a variety of Linux application servers; including but not limited to nginx, Apache, MySQL, MailScanner, Sendmail, Postfix, Drupal, Aegir, Shibboleth, and Jenkins.
\item Repsonsible for deployment and maintence of ASU's Drupal infastructure, serving over 350 sites
\end{rSubsection}

\begin{rSubsection}{Appalachian State University TSS - Walkin Center}{September 2003 - February 2010
}{PC and Mac Technician}{Boone, NC}
\item Serviced PC and Macintosh hardware and software; provided training and support.
\item Developed diagnostic and storage systems running on Linux.
\item Apple Customer Service Excellence awards.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University Physics and Astronomy}{August 2007 - May 2008}{System Administrator}{Boone, NC}
\item Deployed and maintained a Mac and Linux classroom server for computational physics.
\item Developed and maintained program that allowed students to submit their work for grading.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University Physics and Astronomy}{May 2007 - May 2008}{Research Intern}{Boone, NC}
\item Used instrumentation available at Dark Sky Observatory and via SkyNet; reduced and analyzed data.
\item Findings published in ICARUS and presented data at SNURCS.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University Physics and Astronomy}{September 2005 - May 2006}{Astronomy Lab TA}{Boone, NC}
\item Instructed students in their lab work including the use of Meade and Celestron SCT telescopes.
\item Answered student questions and provided understanding of basic astronomical concepts.
\end{rSubsection}

\begin{rSubsection}{Apple, Inc.}{May 2005 - September 2006}{Mac Specialist}{Durham, NC}
\item Advised and set up customers with Apple products.
\item Developed and presented workshops on using and developing software for the Mac platform.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & C, Java, Python, Objective-C, X86 \& 8051 ASM, VB\\
Network Services & ISC-DHCP, BIND DNS, SMTP, IMAP, HTTP, LDAP\\
Databases \& Data Storage & MySQL, PostgreSQL, redis \\
Network Storage & NFS, Samba, Netatalk, NetApp\\
Web Servers & nginx, Apache\\
Enterprise SSO & Shibboleth, Cosign\\
Content Management & Drupal, MediaWiki, Koken\\
Virtualization & VMWare, Xen, KVM, VirtualBox\\
Science, Statistics and Math & IRAF, Mira, Maple, MatLab, Octave, R, gnuplot\\
Authoring and Publishing & \LaTeX, Markdown, Office \\
\end{tabular}

\end{rSection}

\begin{rSection}{Publications}

\textbf{Insights on the Binary Asteroid 121 Hermione} with P. Descamps, J. Pollock, J. Green, et. al; Published 09/2009 ICARUS
\end{rSection}

\begin{rSection}{Awards}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
LaFayette Memorial Scholarship & 2003 \\
Wrenn Memorial Scholarship & 2003-2005 \\
Sigma Pi Sigma Physics Honors Society & 2010 \\
Appalachian Mountain Photography Contest Finalist & 2012 \\
\end{tabular}

\end{rSection}

\begin{rSection}{Interests and Involvement}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
ASU Gaming Club & Club Advisor \\
ASU Linux Users Group & Member \\
ASU Mac Users Group & President \\
Blue Ridge Photo Fest & Organizer and Leader \\
Dark Sky Observatory & Assisted with Monthly Outreach Programs \\
Ashe Camera Club & Member and Presenter \\

\end{tabular}

\end{rSection}

\begin{rSection}{References}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
James Shook - IT Manager & (828) 262-6266 \\
Dr. Joe Pollock - Astronomy Professor & (828) 262-2433 \\
Justin Cervero - Senior System Administrator & (828) 262-6199 \\

\end{tabular}

\end{rSection}

\end{document}
