%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{cv} % Use the custom cv.cls style
\usepackage{lmodern}
\usepackage{xeCJK}
\usepackage[left=0.75in,top=0.25in,right=0.75in,bottom=0.25in]{geometry} % Document margins
\usepackage{hyperref}
\name{Leander Hutton} % Your name
\address{leander@one-button.org | {www.one-button.org}}
\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	{\bf Appalachian State University} \hfill {\em Degree Awarded - May 2011} \\ 
	{\em Masters of Science in Physics and Laboratory Automation} \\
	Member of Sigma Pi Sigma - Physics Honors Society \\
	
	{\bf Appalachian State University} \hfill {\em Degree Awarded - May 2008} \\ 
	{\em Bachelor of Science in Physics and Astronomy} \\
	{\em Minor in Japanese - course requirements completed after graduation}\hfill{\em Dec 2022}\\
	{\em Insights on the Binary Asteroid 121 Hermione} \hfill {\em Sept 2009} \\ {P. Descamps, J. Pollock, J. Green, et.al;}
	
	
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Appalachian State University ITS - NICS}{November 2013 - Present}{Network Specialist}{Boone, NC}
\item Configure and maintain Ansible for configuration management and new host deployment.
\item Built transparent OpenVPN tunnels for remote campuses using Debian.
\item Developed OpenVPN authentication program in Python to integrate with 2FA for road warrior connections.
\item Created host and application RHEL/Debian/Ubuntu deployment and management playbooks with Ansible across hardware, virtual and cloud platforms. Managed application servers on KVM.
\item Work with the team testing and maintaining Jira and our Agile practices.
\item Install and maintain a variety of applications; including but not limited to nginx, Apache, MySQL, OpenVPN, Cacti, Nagios, and PostgreSQL on Linux.
\item Provide tier two support to end users upon fronline support agent's request.

\end{rSubsection}

\begin{rSubsection}{Appalachian State University Physics and Astronomy}{August 2013 - May 2018}{Adjunct Faculty - Astronomy Lab Instructor}{Boone, NC}
\item Teaching introductory astronomy concepts to students; providing and evaluating hands-on exercises.
\item Operated the Rankin GoTo Astronomy Lab consisting of several Celestron SCTs and SBIG imaging cameras.
\item Setup the video stream for the 2017 solar eclipse, configured software and hardware.
\item Assisted in the management of the labrartory dekstop software stack in Linux and Windows 7.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University ITS - Enterprise Systems}{February 2010 - November 2013}{Operations and Systems Analyst}{Boone, NC}
\item Performed system administration tasks on Red Hat Enterprise Linux (RHEL) based systems.
\item Installed and maintained a variety of GNU/Linux application servers; including but not limited to nginx, Apache HTTPD, MySQL, MailScanner, Sendmail, Postfix, Drupal, Aegir, Shibboleth, and Jenkins.
\item Responsible for deployment and maintenance of ASU's Drupal infastructure, serving over 350 sites.
\item Created a Python program for automatic password changing and locking of suspected phished accounts.
\item Re-based SMTP system on postfix from sendmail. 
\end{rSubsection}

\begin{rSubsection}{Appalachian State University TSS - Walk-in Center}{September 2003 - February 2010
}{PC and Mac Technician}{Boone, NC}
\item Serviced PC and Macintosh hardware and software; provided training and support.
\item Developed diagnostic and storage systems running on GNU/Linux.
\item Apple Customer Service Excellence awards.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University Physics and Astronomy}{August 2007 - May 2008}{System Administrator}{Boone, NC}
\item Deployed and maintained a Mac and GNU/Linux classroom server for computational physics.
\item Developed and maintained a program that allowed students to submit their work for grading.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University Physics and Astronomy}{May 2007 - May 2008}{Research Intern}{Boone, NC}
\item Used instrumentation available at Dark Sky Observatory and via SkyNet; reduced and analyzed data for publication.
\item Presented research and UNC Greensboro and Appalachian State.
\end{rSubsection}

\begin{rSubsection}{Appalachian State University Physics and Astronomy}{September 2005 - May 2006}{Astronomy Lab TA}{Boone, NC}
\item Instructed students in their lab work including the use of Meade and Celestron SCT telescopes.
\item Answered student questions and provided understanding of basic astronomical concepts.
\end{rSubsection}

\begin{rSubsection}{Apple, Inc.}{May 2005 - September 2006}{Mac Specialist}{Durham, NC}
\item Advised and set up customers with Apple products.
\item Developed and presented workshops on using and developing software for the Mac platform.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming and Script Languages & C, bash, Python, X86 \& 8051 ASM \\
Development and Version Control & subversion, git, gitolite \\
Networking & ISC-DHCP, BIND, dnsmasq, OpenVPN, iptables, nftables, pf\\
Email & postfix, dovecot, sendmail, amavis\\
Databases & MySQL, MariaDB, PostgreSQL, redis  \\
Data Storage & NFS, CIFS, Netatalk, ZFS, BTRFS, Linux md\\
Web Servers & nginx, Apache\\
Content Management & Drupal, MediaWiki, Pelican\\
Virtualization and Containers & Xen, KVM, VirtualBox, Vagrant, OpenVZ, Docker, Podman \\
Configuration Management & Ansible \\ 
Science, Statistics and Math & IRAF, Maple, MatLab, Octave, R, gnuplot\\
Authoring and Publishing & \LaTeX, Markdown, Office\\
Photo and Video & Vegas, Final Cut, Kdenlive, Darktable, GIMP\\
\end{tabular}
\end{rSection}

\begin{rSection}
{Presentations and Public Speaking}
{Binary Asteroid Light Curves}\hfill{SNCURS - October 2009}\\
{Darktable: Digital Photo Processing on Linux}\hfill{SouthEast LinuxFest - June 2022}\\
{写真術における日本の影響 (Japenese Influence on Photography)}\hfill{W2A Conference - October 29, 2022}
\end{rSection}


\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }

\end{tabular}

\begin{rSection}{Interests, Involvement and Awards}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
ASU Gaming Club & Club Advisor\\
ASU Linux Users Group & Member\\
Western NC Linux Users Group & Member and Presenter\\
Blue Ridge Photo Fest & Organizer\\
ASU Dark Sky Observatory & Assisted with Monthly Outreach Programs\\
Electronic Frontier Foundation & Member\\
Repair Association & Member\\
National Association for Amateur Radio (ARRL) & Member\\
Watauga County Beekeeping Association & Member \\
Ashe Camera Club & Member and Presenter\\
LaFayette Memorial Scholarship & 2003 \\
Wrenn Memorial Scholarship & 2003-2005 \\
Sigma Pi Sigma Physics Honors Society & 2010 \\
Appalachian Mountain Photography Contest Finalist & 2012 \\


\end{tabular}

\end{rSection}

\end{document}
