\documentclass{new_cv} % Use the custom new_cv.cls style
\usepackage{xeCJK}
\usepackage{multicol}
\usepackage[left=1.00in,top=0.5in,right=1.00in,bottom=1.00in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{xhfill}

% Font
\usepackage{tgbonum}
\usepackage[T1]{fontenc}

\begin{document}
	\begin{multicols}{2}
			{\Huge \bfseries  Leander Hutton}  
			\begin{flushright}
					{\bfseries leander@one-button.org \\ \bfseries www.one-button.org}\\
			\end{flushright}

	     \end{multicols}

% Education Section
\begin{rSection}{Education}
	
	{\bf \color{NavyBlue} Physics and Laboratory Automation, Master of Science}\hfill {\em May 2011} \\ 
	{\em Appalachian State University} \\
	Member of Sigma Pi Sigma - Physics Honors Society \\

	{\bf  \color{NavyBlue} Physics and Astronomy, Bachelor of Science}\hfill {\em May 2008} \\ 
	{\em Appalachian State University} \\
	Requirements for Japanese Minor completed after graduation\hfill{\em Dec 2022}\\
	{\em Insights on the Binary Asteroid 121 Hermione} \hfill {\em Sept 2009}\\ {P. Descamps, J. Pollock, J. Green, et.al;}	
\end{rSection}

\begin{rSection}{Work Experience}
	
 {\bf  {Appalachian State University ITS}} \hfill {Boone, NC}
 
   \begin{rSubsection}{Systems Engineer}{July 2022 - Current}
	\item Developed and deployed RHEL based HPC cluster with Slurm and Apptainer/Singularity.
	\item Deployed Rstudio and Posit Connect for research computing on RHEL.
 	\item Adobe Creative Cloud administration, migrated to Azure AD sync.
 	\item JAMF 100 Certification.
 	\item Linux Foundation Kubernetes Administrator training.
 	\item Continued maintaining Debian, Ubuntu and RHEL based servers.
 \end{rSubsection}

      \begin{rSubsection}{Network Specialist}{November 2013 - July 2022}
		\item Deployed and maintained Ansible for configuration management.
		\item Built transparent OpenVPN tunnels for remote campuses using Debian.
		\item Developed OpenVPN authentication program in Python to integrate with AD and Duo 2FA.
		\item Maintain Cacti graphing instance on FreeBSD and later Deban.
        \item Provide tier two support to end users.
      \end{rSubsection}
      
      \begin{rSubsection}{Operations and Systems Analyst}{February 2010 - November 2013}
		\item Performed system administration tasks on Red Hat Enterprise Linux (RHEL) based systems.
		\item Email administration: MailScanner, Sendmail, Postfix, Dovecot IMAP. 
		\item Setup initial MySQL cluster.
		\item Deployed and maintained Drupal infrastructure, serving over 350 sites.
		\item Created a Python program for automatic locking of suspected phished accounts.
		\item Migrated SMTP servers from Sendmail to Postfix.
       \end{rSubsection}
     
         \begin{rSubsection}{PC and Mac Tech}{August 2003 - January 2010}
   \item Serviced PC and Macintosh hardware and software; provided training and support.
   \item Developed diagnostic and storage systems running on Linux.
   \item Received Apple Customer Service Excellence awards.
   \end{rSubsection}
   
     {\bf {Appalachian State University Physics \& Astronomy}} \hfill { Boone, NC}
   
          \begin{rSubsection}{Adjunct Astronomy Faculty}{August 2013 - May 2018}
           \item Teaching introductory astronomy concepts to students; providing and evaluating hands-on exercises.
          \item Operated the Rankin GoTo Astronomy Lab consisting of several Celestron SCTs and SBIG imaging cameras.
\item Setup the video stream for the 2017 solar eclipse, configured software and hardware.
\item Assisted in the management of the laboratory desktop software stack in Linux and Windows 7.
   \end{rSubsection}
   
      \begin{rSubsection}{System Administrator}{August 2007 - May 2008}
   	\item Deployed and maintained a Mac and Linux classroom server for computational physics.
   	\item Developed a program that allowed students to submit their work for grading.
   \end{rSubsection}
   
     \begin{rSubsection}{Research Intern}{May 2007 - May 2008}
   	\item Used instrumentation available at Dark Sky Observatory and via SkyNet; reduced and analyzed data for publication.
   	\item Created poster presentation for asteroid research.
   	\item Presented research and UNC Greensboro and Appalachian State.
   \end{rSubsection}
   
        \begin{rSubsection}{Astronomy Lab TA}{September 2005 - May 2006}
   	\item Instructed students in their lab work including the use of Meade and Celestron SCT telescopes.
   	\item Answered student questions and provided understanding of basic astronomical concepts.
   \end{rSubsection}
  
  {\bf {Apple, Inc}} \hfill { Durham, NC}
   
    \begin{rSubsection}{Mac Specialist}{May 2005 - September 2006}
   	\item Advised and set up customers with Apple products.
   	\item Developed and presented workshops on using and developing software for the Mac platform.
   \end{rSubsection}
   
   \end{rSection}
   


\begin{rSection}{Skills}
	{\bf Languages:} English (Native),  Intermediate Japanese  \\
	{\bf Operating Systems:} Debian, Ubuntu, Red Hat Enterprise, FreeBSD, Fedora, macOS, Windows \\
	{\bf Digital Photo \& Video Software:}  darktable, GIMP, Photoshop, Adobe Camera RAW, DaVinci Resolve, Kdenlive, Final Cut \\
	{\bf Photo and Video Systems:} {Nikon Digital, Fuji Digital, Mamiya 645, GoPro } \\
	{\bf Programming and Scripting:}  Python, bash, ksh, R, CSS, C, Intel ASM \\
	{\bf Advanced File Systems:} OpenZFS, BTRFS \\
	{\bf Containers \& Virtualization:} Xen, KVM, VMware, Kubernetes, Podman, Apptainer, Singularity \\
	{\bf Project Management:} Jira, Redmine \\
	{\bf Databases \& DB Like:} MySQL, PostgresSQL, sqlite, redis \\
	{\bf Document Preparation:} \LaTeX, Office, Markdown
\end{rSection}

\pagebreak

\begin{rSection}
	{Presentations and Public Speaking}
	{Binary Asteroid Light Curves}\hfill{SNCURS - {\em October 2009}}\\
	{Photography Basics}\hfill{Catchlight Gallery - {\em Summer 2013}}\\
	{Darktable: Digital Photo Processing on Linux}\hfill{South East Linux Fest - {\em June 2022}}\\
	{写真術における日本の影響}\hfill{W2A Conference - {\em October 2022}}\\
	{日本人の彗星の狩り}\hfill{Appalachian State University - {\em April 2023}}
\end{rSection}

\begin{rSection}
	{Involvement}
	\begin{list}{$\cdot$}{\leftmargin=1em}\itemsep -0.5em \vspace{-0.5em} 
		\item {Volunteer firefighter with Todd Volunteer Fire Department, assist with technical duties as well.}
		\item {Club advisor for the AppState Gaming Club.}
		\item {Contribute to testing, bug reports and how-to videos for darktable, an open source RAW photo developer.}
		\item {Create presentations for local Linux User Groups on various topics.}
		\item {Amateur radio operator, General Class call sign KM4AZD, Watauga Radio Club member.}
		\item {Volunteer for ASU Dark Sky Observatory Public public nights and outreach.}
	\end{list}
	\vspace{0.5em}
\end{rSection}

\begin{rSection}{Memberships and Awards}
Blue Ridge Photo Fest \hfill Organizer\\
Electronic Frontier Foundation  \hfill  Member\\
National Association for Amateur Radio (ARRL)  \hfill  Member\\
Watauga County Beekeeping Association  \hfill  Member \\
LaFayette Memorial Scholarship \hfill  2003 \\
Wrenn Memorial Scholarship  \hfill  2003-2005 \\
Sigma Pi Sigma Physics Honors Society  \hfill  2010 \\
Appalachian Mountain Photography Contest Finalist  \hfill  2012 \\
\end{rSection}

\end{document}
