
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
	\item\small{
		{#1}
	}
}


% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item[]
    \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\small#3} & \textit{\ #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://www.one-button.org}{\Large Leander Hutton}}& \href{mailto:leander@one-button.org}{leander@one-button.org}\\&
  \href{https://www.one-button.org}{http://www.one-button.org}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Appalachian State University}{Boone, NC}
      {Master of Science in Engineering Physics}{2008-2011}
    \resumeSubheading
      {Appalachian State University}{Boone, NC}
      {Bachelor of Science in Physics}{2003-2008}
\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Appalachian State University ITS}{Boone, NC}
      {Network Specialist}  {Nov 2013 - Present}
      \resumeItemListStart
        \resumeItem{Configure and maintain Ansible for configuration management and new host deployment}
        \resumeItem{Built transparent OpenVPN tunnels for remote campuses using Debian and RHEL.}
        \resumeItem{Developed OpenVPN authentication program in Python to integrate with 2FA for road warrior connections.}
        \resumeItem{Created host and application RHEL/Debian/Ubuntu deployment and manaagement playbooks with Ansible across hardware, virtual and cloud platforms. Managed application servers on KVM.}
        \resumeItem{Work with the team testing and maintaining Jira and our Agile practices.}
      \resumeItemListEnd       
    \resumeSubSubheading
     {Operations and Systems Analyst}{Feb 2010 - Nov 2013}
    \resumeItemListStart
       \resumeItem{Performed system administration tasks on Red Hat Enterprise Linux (RHEL) based systems.}
       \resumeItem{Installed and maintained a variety of GNU/Linux application servers; including but not limited to nginx, Apache HTTPD, MySQL, MailScanner, Sendmail, Postfix, Drupal, Aegir, Shibboleth, and Jenkins.}
       \resumeItem{Responsible for deployment and maintenance of ASU's Drupal infastructure, serving over 350 sites.}
       \resumeItem{Created a Python program for automatic password changing and locking of suspected phished accounts.}
       \resumeItem{Re-based SMTP system on postfix from sendmail.}
   \resumeItemListEnd
	\resumeSubheading
	{Appalachian State University Physics and Astronomy}{Boone, NC}
	{Adjunct Faculty}  {Aug 2013 - May 2018}
	\resumeItemListStart
	 \resumeItem{Teaching introductory astronomy concepts to students; providing and evaluating hands-on exercises.}
	 \resumeItem{Operated the Rankin GoTo Astronomy Lab consisting of several Celestron SCTs and SBIG imaging cameras.}
	 \resumeItem{Setup the video stream for the 2017 solar eclipse, configured software and hardware.}
	\resumeItem{Assisted in the management of the labrartory dekstop software stack in Linux and Windows 7.}
	 \resumeItemListEnd
	 \resumeSubSubheading
	 {System Administrator}{August 2007 - May 2008}
	 \resumeItemListStart
	 \resumeItem{Deployed and maintained a Mac and GNU/Linux classroom server for computational physics.}
	 \resumeItem{Developed and maintained a program that allowed students to submit their work for grading.}
	 \resumeItemListEnd
	 \resumeSubSubheading
	 {Research Intern}{May 2007 - May 2008}
	 \resumeItemListStart
	 \resumeItem{Used instrumentation available at Dark Sky Observatory and via SkyNet; reduced and analyzed data for publication.}
	 \resumeItem{Presented research and UNC Greensboro and Appalachian State.}
	 \resumeItemListEnd
	 \resumeSubheading
	 {Appalachian State University TSS}{Boone NC}
	 {PC and Mac Technician}{Aug 2003 - Feb 2010}
	 \resumeItemListStart
	 \resumeItem{Serviced PC and Macintosh hardware and software; provided training and support.}
	 \resumeItem{Developed diagnostic and storage systems running on GNU/Linux.}
	 \resumeItem{Apple Customer Service Excellence awards.}
	 \resumeItemListEnd
	 

\resumeSubHeadingListEnd

   


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
    \resumeSubItem{Mac Setup}
      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

