
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Leander Hutton} \\ \vspace{1pt}
    \small +1 (828) 719-7826 $|$ \href{mailto:leander@leander@one-button.org}{\underline{leander@one-button.org}} 
  %  \href{https://one-button.org}{\underline{www.one-button.org}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Network Specialist}{November 2013-- Present}
      {Appalachian State University ITS}{Boone, NC}
      \resumeItemListStart
        \resumeItem{Performed system administration tasks on Debian GNU/Linux, RHEL, and BSD systems.}
        \resumeItem{Installed and maintained a variety of applications; including but not limited to nginx, Apache, MySQL, OpenVPN, Cacti, MRTG, and PostgreSQL.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Adjunct Faculty - Astronomy Lab Instructor}{August 2013 - May 2018}
      {Appalachian State University Physics and Astronomy}{Boone, NC}
      \resumeItemListStart
        \resumeItem{Taught introductory astronomy concepts to students; provided and evaluating hands-on exercises.}
            \resumeItemListEnd

    \resumeSubheading
      {Operations and System Analyst}{February 2010 - November 2013}
      {Appalachian State University ITS}{Boone, NC}
      \resumeItemListStart
       \resumeItem{Installed and maintained a variety of GNU/Linux application servers; including but not limited to nginx, Apache, MySQL, MailScanner, Sendmail, Postfix, Drupal, Aegir, Shibboleth, and Jenkins.}
      \resumeItemListEnd
     \resumeSubheading
      {PC and Mac Technician}{September 2003 - February 2010}
      {Appalachian State University TSS}{Boone, NC}
      \resumeItemListStart
      \resumeItem{Serviced PC and Macintosh hardware and software; provided training and support. Apple Customer Service Excellence awards. Developed diagnostic and storage systems. }
      \resumeItemListEnd
      \resumeSubheading
      {System Administrator}{August 2007 - May 2008}
      {Appalachian State University Physics and Astronomy}{Boone, NC}
      \resumeItemListStart
      \resumeItem{ Deployed Mac and GNU/Linux servers for computational physics class, developed system for assignment submission. }
      \resumeItemListEnd
      \resumeSubheading
      {Research Intern}{May 2007 - May 2008}
      {Appalachian State University Physics and Astronomy}{Boone, NC}
      \resumeItemListStart
      \resumeItem {Used instrumentation available at Dark Sky Observatory and via SkyNet; reduced and analyzed data. Published 09/2009 ICARUS. }
      \resumeItemListEnd
      \resumeSubheading
      {Astronomy Lab TA}{September 2005 - May 2006}
      {Appalachian State University Physics and Astronomy}{Boone, NC}
      \resumeItemListStart
      \resumeItem {Instructed students in their lab work including the use of Meade and Celestron SCT telescopes.}
      \resumeItemListEnd
      \resumeSubheading
      {Mac Specialist}{May 2005 - September 2006}
      {Apple Computer, Inc}{Durham, NC}
      \resumeItemListStart
      \resumeItem {Advised and set up customers with Apple products, developed and presented workshops. }
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Development}{: C, Python, Java, X86 and 8051 ASM, Visual Studio, git, gitolite} \\
     \textbf{Networking}{: ISC-DHCP, BIND, dnsmasq. OpenVPN, iptables, nftables, pf} \\
     \textbf{Email Administration}{: postfix, dovecot, sendmail, amavis} \\
     \textbf{Database}{: MySQL, MariaDB, PostgreSQL, redis} \\
     \textbf{Data Storage}{: NFS, CIFS, Netatalk, ZFS, BTRFS, Linux md} \\
     \textbf{Web}{: nginx, Apache, Drupal, MediaWiki, Pelican} \\
     \textbf{Virtualization and Management}{: Xen, KVM, libvirt, Ansible, Vagrant  } \\
     \textbf{Science and Math}{: IRAF, Maple, MatLab, GNU/Octave, R, gnuplot} \\
     \textbf{Desktop Software}{: GNOME, KDE Plasma, \LaTeX, Markdown, Office, Kdenlive, Vegas, Darktable, GIMP, Adobe} 
    }}
 \end{itemize}

%-----------INTERESTS-----------
\section{Interests, Memberships, Awards and Involvement }
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
			\textbf{Free Software Foundation}{: Associate Member} \\
			\textbf{Electronic Frontier Foundation}{:  Member} \\
			\textbf{The Repair Association}{: Member} \\
			\textbf{Blue Ridge Photofest}{: Organizer and Presenter} \\
			\textbf{Simga Pi Sigma Physics Honor Society}{: Inducted 2010} \\
         	\textbf{Dark Sky Observatory}{: Outreach Volunteer} \\
         	\textbf{Amateur Radio License KM4AZD, General Class}{: 2014} \\
         	\textbf{LaFayette Memorial Scholarship}{: 2003} \\
         	\textbf{Wrenn Memorial Scholarship}{: 2003-2005} \\
	}}
\end{itemize}


%


%-------------------------------------------
\end{document}

